### 2024-07-17 ms.qmd
Updates

@@

@@

>>>>

```{r}
#| label: setup
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, ggh4x, PupillometryR, cowplot, png, grid)
```

@@

```{r, data_metrics}
#| label: data_metrics
# Using the raw learning database, I calculate here some basic metrics mentioned later in the Methdos (see below).
data <- read.csv(here("./data/Spatial_learn.csv"))
#
# Total number of clutches
total_clutches <- data %>% 
  distinct(clutch) %>% 
  count() %>% 
  pull(n)
# Calculate total number of individuals
total_individuals <- data %>% 
  distinct(lizard_id) %>% 
  count() %>% 
  pull(n)
# Calculate number of individuals per clutch
individuals_per_clutch <- data %>%
  distinct(lizard_id, clutch) %>%
  group_by(clutch) %>%
  summarize(individual_count = n())
```

@@

There are a total of  `r total_individuals`, and `r total_clutches` clutches in the database. The average number of individuals per clutch is `r mean(individuals_per_clutch)`, with a minimum of `r min(individuals_per_clutch)` individuals per clutch (`r sum(individuals_per_clutch$individual_count == max(individuals_per_clutch$individual_count))` clutches) and a maximum of `r sum(individuals_per_clutch$individual_count == min(individuals_per_clutch$individual_count))` ( clutches).
